---
title: "青少人困擾與背景關連"
output: html_notebook
---

#資料來源、載入所需套件
```{r}
rm(list=ls())
load("j3.Rdata")

library(magrittr)
library(knitr)
library(dplyr)
```

### cheat vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態))-> j4


```

### cheat vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```

### cheat vs male 
以下均依cheat vs locationschool程式碼，但把A、B變名依以下定義改變, 名的部份會有''號:  

A變-cheat
A名-'cheat'
B變-male
B名-'male'


```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```

以下類推所有cheat可能背景交叉組合

### cheat vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### cheat vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(cheat),na.rm=TRUE),
            問題類別='cheat',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```

接著移到下個青少年問題：drug
### drug vs urbanshool
A變-drug
A名-'drug'
B變-urbanshool
B名-'urbanshool'
###j3 %>% group_by(B變) %>%
  summarise(問題比例=mean(as.numeric(A變),na.rm=TRUE),
            問題類別=A名,
            背景分群依據=B名) %>%
  rename(背景分群狀態=B名) %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4

### drug vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```

### drug vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### drug vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### drug vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(drug),na.rm=TRUE),
            問題類別='drug',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```

### leavehome vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```

### leavehome vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### leavehome vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### leavehome vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### leavehome vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(leavehome),na.rm=TRUE),
            問題類別='leavehome',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```




### skipclass vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4



```

### skipclass vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### skipclass vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### skipclass vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### skipclass vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(skipclass),na.rm=TRUE),
            問題類別='skipclass',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4



```

### damage vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### damage vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### damage vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### damage vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(damage),na.rm=TRUE),
            問題類別='damage',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```




### steal vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4



```

### steal vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### steal vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### steal vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### steal vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(steal),na.rm=TRUE),
            問題類別='steal',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```



### sexualbehavior vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4



```

### sexualbehavior vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### sexualbehavior vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### sexualbehavior vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### sexualbehavior vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(sexualbehavior),na.rm=TRUE),
            問題類別='sexualbehavior',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```



### wound vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4



```

### wound vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### wound vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### wound vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### wound vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(wound),na.rm=TRUE),
            問題類別='wound',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```




### blackmail vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4



```

### blackmail vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### blackmail vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### blackmail vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### blackmail vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(blackmail),na.rm=TRUE),
            問題類別='blackmail',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```




### smokingdrunk vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4



```

### smokingdrunk vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### smokingdrunk vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### smokingdrunk vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### smokingdrunk vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(smokingdrunk),na.rm=TRUE),
            問題類別='smokingdrunk',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```



### betelnut vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4



```

### betelnut vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### betelnut vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### betelnut vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### betelnut vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(betelnut),na.rm=TRUE),
            問題類別='betelnut',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```




### drug2 vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4



```

### drug2 vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### drug2 vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### drug2 vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### drug2 vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(drug2),na.rm=TRUE),
            問題類別='drug2',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```




### fleehome vs. urbanshool
```{r}
j3 %>% group_by(urbanshool) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='urbanshool') %>%
  rename(背景分群狀態='urbanshool') %>%
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4



```

### fleehome vs locationschool
```{r}
j3 %>% group_by(locationschool) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='locationschool') %>%
  rename(背景分群狀態='locationschool') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### fleehome vs male 
```{r}
j3 %>% group_by(male) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='male') %>%
  rename(背景分群狀態='male') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4
```


### fleehome vs age
```{r}
j3 %>% group_by(age) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='age') %>%
  rename(背景分群狀態='age') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs f_life
```{r}
j3 %>% group_by(f_life) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='f_life') %>%
  rename(背景分群狀態='f_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs f_live
```{r}
j3 %>% group_by(f_live) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='f_live') %>%
  rename(背景分群狀態='f_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs f_edu
```{r}
j3 %>% group_by(f_edu) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='f_edu') %>%
  rename(背景分群狀態='f_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs m_life
```{r}
j3 %>% group_by(m_life) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='m_life') %>%
  rename(背景分群狀態='m_life') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs m_live
```{r}
j3 %>% group_by(m_live) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='m_live') %>%
  rename(背景分群狀態='m_live') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs m_edu
```{r}
j3 %>% group_by(m_edu) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='m_edu') %>%
  rename(背景分群狀態='m_edu') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs income_mon
```{r}
j3 %>% group_by(income_mon) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='income_mon') %>%
  rename(背景分群狀態='income_mon') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs f_nativep
```{r}
j3 %>% group_by(f_nativep) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='f_nativep') %>%
  rename(背景分群狀態='f_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs m_nativep
```{r}
j3 %>% group_by(m_nativep) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='m_nativep') %>%
  rename(背景分群狀態='m_nativep') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs pa_marriage
```{r}
j3 %>% group_by(pa_marriage) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='pa_marriage') %>%
  rename(背景分群狀態='pa_marriage') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs livewithwhom
```{r}
j3 %>% group_by(livewithwhom) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='livewithwhom') %>%
  rename(背景分群狀態='livewithwhom') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs child_count
```{r}
j3 %>% group_by(child_count) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='child_count') %>%
  rename(背景分群狀態='child_count') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs divorce
```{r}
j3 %>% group_by(divorce) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='divorce') %>%
  rename(背景分群狀態='divorce') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```
### fleehome vs paquarrel
```{r}
j3 %>% group_by(paquarrel) %>%
  summarise(問題比例=mean(as.numeric(fleehome),na.rm=TRUE),
            問題類別='fleehome',
            背景分群依據='paquarrel') %>%
  rename(背景分群狀態='paquarrel') %>% 
  mutate(背景分群狀態=as.character(背景分群狀態)) %>%
  rbind(.,j4) -> j4


```



